\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage[hidelinks]{hyperref}
\graphicspath{{figures/}}

%% ---- TU Delft & report colours ----
\definecolor{tudelft-dark}{RGB}{0,51,102}
\definecolor{hpcolor}{RGB}{0,100,180}
\definecolor{eecolor}{RGB}{0,128,0}
\newcommand{\micron}{\textmu m}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

%% ================================================================
%%  COVER PAGE  (does NOT count toward the 6-page body limit)
%% ================================================================
\onecolumn
\pagenumbering{Roman}
\thispagestyle{empty}

\begin{center}
  \vspace*{0.5cm}
  {\Large\textbf{Delft University of Technology}}\\[0.15cm]
  {\normalsize Faculty of Electrical Engineering, Mathematics and Computer Science}\\[1.5cm]

  {\LARGE\textbf{ET4351 Digital VLSI Systems on Chip}}\\[0.15cm]
  {\Large Project Report\,---\,Academic Year 2025/2026}\\[2cm]

  {\Huge\textbf{Group\,\color{red}XX}}\\[1cm]
\end{center}

\vspace{0.6cm}

%% ---- Member Table ----
\noindent\textbf{\large Team Members \& Individual Contributions}

\vspace{2pt}

\noindent
{\small\renewcommand{\arraystretch}{0.95}
\begin{tabularx}{\textwidth}{|c|l|l|c|X|}
\hline
\rowcolor{lightgray}
\textbf{\#} & \textbf{First Name} & \textbf{Last Name} & \textbf{Student ID} & \textbf{Individual Contribution} \\
\hline
1  & & & & \\
\hline
2  & & & & \\
\hline
3  & & & & \\
\hline
4  & & & & \\
\hline
5  & & & & \\
\hline
6  & & & & \\
\hline
7  & & & & \\
\hline
8  & & & & \\
\hline
9  & & & & \\
\hline
10 & & & & \\
\hline
\end{tabularx}
}

\vspace{1pt}
\noindent{\scriptsize\textit{``Primary Responsibility'': briefly state each member's main contribution (e.g., ``Butterfly unit RTL'', ``Genus synthesis \& clock gating'', ``Post-layout sim \& VCD'').}}

\vspace{6pt}

%% ---- Guidelines Box ----
\noindent\fcolorbox{tudelft-dark}{lightgray}{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{3pt}
\begin{center}
{\large\bfseries\color{tudelft-dark} Report Guidelines \& Knock-Out Criteria}
\end{center}
\vspace{2pt}

{\small
\begin{enumerate}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \item \textbf{Format:} IEEE double-column, compiled to PDF. Font size: 10\,pt (IEEE default). Use this template.

    \item \textbf{Page limit:} The main body (Sections~I--IV) must fit within
        \textbf{6~pages} ($\approx$3~pages per design). This cover page and all
        appendices are \textbf{excluded} from the page count.

    \item \textbf{Structure:} You \textbf{must} follow the mandatory section structure defined in this template. Do not add, remove, or rename top-level sections (I--IV).

    \item \textbf{Two designs:} Present both a \textcolor{hpcolor}{\textbf{High-Performance~(HP)}} and an \textcolor{eecolor}{\textbf{Energy-Efficient~(EE)}} accelerator. Shared aspects should be described once; per-design subsections are provided.
        \textbf{Targets at 12\,MHz:}
        \textcolor{hpcolor}{HP\,---\,latency ${<}\,61.00\,\mu$s} (baseline);
        \textcolor{eecolor}{EE\,---\,accelerator power ${<}\,0.403$\,mW} (baseline).
        Clock period is \textbf{free to change}.

    \item \textbf{Submission checklist} (all mandatory):
    \begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, leftmargin=2em]
        \item[\ding{113}] Report (PDF) with cover page filled in
        \item[\ding{113}] SystemVerilog/Verilog source files (cleaned \& commented)
        \item[\ding{113}] All synthesis and P\&R scripts
        \item[\ding{113}] \texttt{finaldesign\_hp/} and \texttt{finaldesign\_ee/} directories (each with \texttt{accel\_audio.hex}, \texttt{et4351.phys.sdf}, \texttt{et4351.phys.v})
        \item[\ding{113}] All signoff reports: included as files in the project zip \textbf{and} as screenshots/excerpts in the PDF appendix
        \item[\ding{113}] Activity annotation and full power reports: included as files in the project zip \textbf{and} as screenshots/excerpts in the PDF appendix
    \end{itemize}

    \item \textbf{Signoff requirements} (per design):
        core area 596.4\,\micron{} $\times$ 596.4\,\micron;~~
        setup \& hold timing clean, fully DRV clean
        (\texttt{max\_tran} violations are acceptable but risky near zero slack);~~
        connectivity, geometry, antenna reports clean;~~
        functionally correct FFT on variable-length audio input.

    \item \textbf{Quality:} Proper use of technical terms. Reasonably proofread. Clean, readable diagrams.

    \item \textbf{Deadline:} Friday, April 10, 2026 at 16:59 CET.
\end{enumerate}
}
\vspace{2pt}
\end{minipage}%
}

\vfill

\begin{center}
{\small\color{darkgray} Academic Year 2025--2026 ~|~ Q3 ~|~}
\end{center}

\clearpage

%% ================================================================
%%  MAIN BODY  (6 pages maximum, pages 1--6)
%% ================================================================
\twocolumn
\pagenumbering{arabic}

\title{ET4351 Project Report\,---\,Group\,{\color{red}XX}}

\author{}

\maketitle

%% ================================================================
\section{\textcolor{hpcolor}{High-Performance (HP) Accelerator}}\label{sec:hp}
%% ================================================================

\subsection{Architecture and Design Methodology}\label{sec:hp:arch}

{\color{hpcolor}Your content here.}

\subsection{Implementation}\label{sec:hp:impl}

{\color{hpcolor}Your content here.}

\subsection{Performance Metrics and Validation}\label{sec:hp:verif}

{\color{hpcolor}Your content here.}

% Example post-layout results table
\begin{table}[htbp]
\caption{Example Post-Layout Results (Please improve or organize in your own way)}
\label{tab:hp_postlayout}
\centering\footnotesize
\begin{tabular}{l r}
  \toprule
  \textbf{Metric} & \textbf{Value} \\
  \midrule
  \multicolumn{2}{l}{\textit{Timing \& Area}} \\
  Frequency               & {\color{hpcolor}XXX\,MHz} \\
  Core Area               & 596.4\,$\mu$m $\times$ 596.4\,$\mu$m \\
  Latency (cycles)        & {\color{hpcolor}XXX} \\
  Latency ($\mu$s)        & {\color{hpcolor}XXX} \\
  \midrule
  \multicolumn{2}{l}{\textit{Sign-off}} \\
  Setup WNS (ns)          & {\color{hpcolor}XXX} \\
  Hold WNS (ns)           & {\color{hpcolor}XXX} \\
  DRC Violations          & {\color{hpcolor}XXX} \\
  DRV Violations          & {\color{hpcolor}XXX} \\
  \midrule
  \multicolumn{2}{l}{\textit{Power (activity-annotated)}} \\
  Dynamic Power            & {\color{hpcolor}XXX\,mW} \\
  Leakage Power            & {\color{hpcolor}XXX\,mW} \\
  Total Power              & {\color{hpcolor}XXX\,mW} \\
  Energy ($P \times T$)    & {\color{hpcolor}XXX\,nJ} \\
  Annotation Coverage      & {\color{hpcolor}XXX\,\%} \\
  \bottomrule
\end{tabular}
\end{table}


%% ================================================================
\section{\textcolor{eecolor}{Energy-Efficient (EE) Accelerator}}\label{sec:ee}
%% ================================================================

\subsection{Architecture and Design Methodology}\label{sec:ee:arch}

{\color{eecolor}Your content here.}

\subsection{Implementation}\label{sec:ee:impl}

{\color{eecolor}Your content here.}

\subsection{Performance Metrics and Validation}\label{sec:ee:verif}

{\color{eecolor}Your content here, including a table similar to Table~\ref{tab:hp_postlayout}.}


%% ================================================================
\section{Comparative PPA Trade-off Analysis}\label{sec:ppa}
%% ================================================================

% Example post-layout PPA comparison table
\begin{table}[htbp]
\caption{Example PPA Comparison (Please improve or organize in your own way)}
\label{tab:ppa}
\centering\footnotesize
\begin{tabular}{l r r r}
  \toprule
  \textbf{Metric} & \textbf{Baseline} & \textcolor{hpcolor}{\textbf{HP}} & \textcolor{eecolor}{\textbf{EE}} \\
  \midrule
  Frequency (MHz)            & 12              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Core Area ($\mu$m$^2$)     & 596.4$^2$       & 596.4$^2$ & 596.4$^2$ \\
  \midrule
  Latency (cycles)           & 732             & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Latency ($\mu$s)           & 61.00           & {\color{hpcolor}--} & {\color{eecolor}--} \\
  \midrule
  Accel. Dynamic Power (mW)         & 0.372              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Accel. Leakage Power (mW)         & 0.013              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Accel. Power (excl. RISC-V) (mW)  & 0.403           & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Total Power (mW)           & 0.626           & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Energy (nJ)                & 2.46           & {\color{hpcolor}--} & {\color{eecolor}--} \\
  \midrule
  Setup WNS (ns)             & --              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Hold WNS (ns)              & --              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  DRC Violations             & --              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  Annotation Coverage (\%)   & --              & {\color{hpcolor}--} & {\color{eecolor}--} \\
  \bottomrule
\end{tabular}
\end{table}

You can discuss the trade-offs revealed by Table~\ref{tab:ppa} and any other relevant observations. For example:
\begin{itemize}
  \item Which architectural and tool-constraint decisions had the largest
        impact on each PPA dimension?
  \item What would you do differently if redesigning?
  \item Any surprising results or lessons learned.
\end{itemize}


%% ================================================================
%%  APPENDIX  (no page limit)
%% ================================================================
\newpage
\onecolumn
\begin{thebibliography}{00}
\bibitem{b1} {A.\ Author, ``Paper title,'' \textit{Journal},
  vol.~X, pp.~Y--Z, Year.}
\bibitem{b2} {B.\ Author, \textit{Book Title}.\ City:
  Publisher, Year.}
\end{thebibliography}

\section*{Appendix}

\subsection*{A.\quad \textcolor{hpcolor}{High-Performance (HP) Design}}\label{app:hp}

\subsubsection*{A.1\quad Timing Reports}\label{app:hp:timing}
\subsubsection*{A.2\quad DRC Reports}\label{app:hp:drc}
\subsubsection*{A.3\quad DRV Reports}\label{app:hp:drv}
\subsubsection*{A.4\quad Connectivity Reports}\label{app:hp:conn}
\subsubsection*{A.5\quad Geometry Reports}\label{app:hp:geom}
\subsubsection*{A.6\quad Antenna Reports}\label{app:hp:antenna}
\subsubsection*{A.7\quad Activity Annotation Reports}\label{app:hp:annotation}
\subsubsection*{A.8\quad Power Analysis Reports}\label{app:hp:power}
\subsubsection*{A.9\quad Sign-off Simulation Waveforms}\label{app:hp:waves}

\subsection*{B.\quad \textcolor{eecolor}{Energy-Efficient (EE) Design}}\label{app:ee}

\subsubsection*{B.1\quad Timing Reports}\label{app:ee:timing}
\subsubsection*{B.2\quad DRC Reports}\label{app:ee:drc}
\subsubsection*{B.3\quad DRV Reports}\label{app:ee:drv}
\subsubsection*{B.4\quad Connectivity Reports}\label{app:ee:conn}
\subsubsection*{B.5\quad Geometry Reports}\label{app:ee:geom}
\subsubsection*{B.6\quad Antenna Reports}\label{app:ee:antenna}
\subsubsection*{B.7\quad Activity Annotation Reports}\label{app:ee:annotation}
\subsubsection*{B.8\quad Power Analysis Reports}\label{app:ee:power}
\subsubsection*{B.9\quad Sign-off Simulation Waveforms}\label{app:ee:waves}

\end{document}
